\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-08-08 forwards-and-backwards.tex
.

    First of all,
    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
    so Lemma \ref{lem:eta_compact_containment}
    shows that our processes satisfy a compact containment condition.
    Secondly, Lemma \ref{lem:eta_projections_tightness}
    shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
    Since the set of finite sums and products of terms of this form
    is dense in the space of bounded continuous functions on $\cmeasures$,
    we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
    Finally,
    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
    any limit point must in fact be in $\measures$,
    and so we have 
    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
\end{proof}

@@

\begin{lemma}[Identifying the limit as a solution to the martingale problem]
    \label{lem:limit_mgale}
    \comment{
        Here we need to check that the martingale property is preserved in the limit.
        But this maybe can be shorter?}
As $N \to \infty$,
$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{N}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{N \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.

>>>>

    First of all,
    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
    so Lemma \ref{lem:eta_compact_containment}
    shows that our processes satisfy a compact containment condition.
    Secondly, Lemma \ref{lem:eta_projections_tightness}
    shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
    Since by the Stone-Weierstrass theorem,
    the algebra of finite sums and products of terms of this form
    is dense in the space of bounded continuous functions on $\cmeasures$,
    we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
    Finally,
    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
    any limit point must in fact be in $\measures$,
    and so we have 
    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
\end{proof}

@@

\begin{lemma}[Identifying the limit as a solution to the martingale problem]
    \label{lem:limit_mgale}
    \comment{Here we need to check that the martingale property is preserved in the limit.}
As $N \to \infty$,
$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{N}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{N \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.
